        \documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath,amsfonts,amssymb,amsthm,commath,dsfont}
\usepackage{enumitem}
\usepackage{framed}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{float}
\usepackage[round]{natbib}
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[breakable]{tcolorbox}
\tcbset{breakable}
\usepackage{mathtools}
\usepackage{subcaption}
%\usepackage{symbols}

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\newcommand{\colbar}{\rule[-3mm]{.3mm}{1.5em}}
\newcommand{\rowbar}{\rule[.5ex]{1.5em}{.3mm}}
\DeclareMathOperator{\rank}{rank}

% following loops stolen from djhsu
\def\ddefloop#1{\ifx\ddefloop#1\else\ddef{#1}\expandafter\ddefloop\fi}
% \bbA, \bbB, ...
\def\ddef#1{\expandafter\def\csname bb#1\endcsname{\ensuremath{\mathbb{#1}}}}
\ddefloop ABCDEFGHIJKLMNOPQRSTUVWXYZ\ddefloop

% \cA, \cB, ...
\def\ddef#1{\expandafter\def\csname c#1\endcsname{\ensuremath{\mathcal{#1}}}}
\ddefloop ABCDEFGHIJKLMNOPQRSTUVWXYZ\ddefloop

% \vA, \vB, ..., \va, \vb, ...
\def\ddef#1{\expandafter\def\csname v#1\endcsname{\ensuremath{\boldsymbol{#1}}}}
\ddefloop ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz\ddefloop

% \valpha, \vbeta, ...,  \vGamma, \vDelta, ...,
\def\ddef#1{\expandafter\def\csname v#1\endcsname{\ensuremath{\boldsymbol{\csname #1\endcsname}}}}
\ddefloop {alpha}{beta}{gamma}{delta}{epsilon}{varepsilon}{zeta}{eta}{theta}{vartheta}{iota}{kappa}{lambda}{mu}{nu}{xi}{pi}{varpi}{rho}{varrho}{sigma}{varsigma}{tau}{upsilon}{phi}{varphi}{chi}{psi}{omega}{Gamma}{Delta}{Theta}{Lambda}{Xi}{Pi}{Sigma}{varSigma}{Upsilon}{Phi}{Psi}{Omega}{ell}\ddefloop

\newcommand\T{{\scriptscriptstyle\mathsf{T}}}
\def\diag{\textup{diag}}



\def\SPAN{\textup{span}}
\def\tu{\textup{u}}
\def\R{\mathbb{R}}
\def\E{\mathbb{E}}
\def\Z{\mathbb{Z}}
\def\be{\mathbf{e}}
\def\nf{\nabla f}
\def\veps{\varepsilon}
\def\cl{\textup{cl}}
\def\inte{\textup{int}}
\def\dom{\textup{dom}}
\def\Rad{\textup{Rad}}
\def\lsq{\ell_{\textup{sq}}}
\def\hcR{\widehat{\cR}}
\def\hcRl{\hcR_\ell}
\def\cRl{\cR_\ell}
\def\hcE{\widehat{\cE}}
\def\cEl{\cE_\ell}
\def\hcEl{\hcE_\ell}
\def\eps{\epsilon}
\def\1{\mathds{1}}
\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}
\def\srelu{\sigma_{\textup{r}}}
\def\vsrelu{\vec{\sigma_{\textup{r}}}}
\def\vol{\textup{vol}}
\def\hw{\textbf{[\texttt{hw2}]}\xspace}
\def\hwcode{\textbf{[\texttt{hw2code}]}\xspace}

\newcommand{\ip}[2]{\left\langle #1, #2 \right \rangle}
\newcommand{\mjt}[1]{{\color{blue}\emph\textbf{[M:}~#1~\textbf{]}}}
\newcommand{\sahand}[1]{{\color{green}\emph\textbf{[Sah:}~#1~\textbf{]}}}


\newtheorem{fact}{Fact}
\newtheorem{lemma}{Lemma}
\newtheorem{condition}{Condition}
\theoremstyle{definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\newenvironment{Q}
{%
	\clearpage
	\item
}
{%
	\phantom{s} %lol doesn't work
	\bigskip
	\textbf{Solution.}
}

\title{CS 446 / ECE 449 --- Homework 2}
\author{\emph{your NetID here}}
\date{}

\begin{document}
	\maketitle
	
	\noindent\textbf{Instructions.}
	\begin{itemize}
		\item
		Homework is due \textbf{\color{red}Tuesday, Feb. 21, at noon CDT}; no late homework accepted.
		
		\item
		Everyone must submit individually at gradescope under \texttt{hw2} and \texttt{hw2code}.
		
		\item
		The ``written'' submission at \texttt{hw2} \textbf{must be typed}, and submitted in
		any format gradescope accepts (to be safe, submit a PDF).  You may use \LaTeX, markdown,
		google docs, MS word, whatever you like; but it must be typed!
		
		\item
		When submitting at \texttt{hw2}, gradescope will ask you to mark out boxes
		around each of your answers; please do this precisely!
		
		\item
		Please make sure your NetID is clear and large on the first page of the homework.
		
		\item
		Your solution \textbf{must} be written in your own words.
		Please see the course webpage for full academic integrity information.
		Briefly, you may have high-level discussions with at most 3 classmates,
		whose NetIDs you should place on the first page of your solutions,
		and you should cite any external reference you use; despite all this,
		your solution must be written in your own words.
		
		\item
		We reserve the right to reduce the auto-graded score for
		\texttt{hw2code} if we detect funny business (e.g., your solution
		lacks any algorithm and hard-codes answers you obtained from
		someone else, or simply via trial-and-error with the autograder).
		
		\item
		When submitting to \texttt{hw2code}, only upload \texttt{hw2\_ResNet.py}. Additional files will be ignored.
		
		\item
		Gradescope coding questions are marked by ``\texttt{[code]}.''
		
	\end{itemize}
	
	
	\begin{enumerate}[font={\Large\bfseries}]
        \input{EM.tex} 
        \input{DeepNet.tex}

        \input{ResNet.tex} 
		
	\end{enumerate}

\newpage

\bibliography{shortbib}
\bibliographystyle{plainnat}

\end{document}
